Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Document Preparation Systems

### 2018-10-04 main.tex
Change Word Processor to Document Preparation System Also deleted the footnote that technically LaTeX is not a WP, since it is no longer needed now.

\addbibresource{./bibliography/Bibliography.bib} 
\hypersetup{
	pdftitle	= {Semantic Preserving Bijective Mappings for Representations of Special Functions in Computer Algebra Systems and Word Processors}
}

@@

\newacronym{dlmf}{DLMF}{Digital Library of Mathematical Functions}
\newacronym{drmf}{DRMF}{Digital Repository of Mathematical Formulae}
\newacronym{cas}{CAS}{Computer Algebra System}
\newacronym{mlp}{MLP}{Mathematical Language Parser}
\newacronym{mlp-pt}{PPT}{PoM-Parsed Tree}
\newacronym{pom-pt}{PPT}{PoM-Parsed Tree}
\newacronym{bnf}{BNF}{Backus-Naur Form}
\newacronym{p2c}{P2C}{Presentation-To-Computation}
\newacronym{nlp}{NLP}{Natural Language Processing}
\newacronym{pom}{PoM}{Part-of-Math}
\newacronym{csv}{CSV}{Comma-Separated Values}
\newacronym{json}{JSON}{JavaScript Object Notation}
\newacronym{teo}{TEO}{Translated Expression Object}
\newacronym{pol}{NPN}{Normal Polish Notation}
\newacronym{rpol}{RPN}{Reverse Polish Notation}
\newacronym{dag}{DAG}{Directed Acyclic Graph}
\newacronym{api}{API}{Application Programming Interface}
\newacronym{mathml}{MathML}{Mathematical Markup Language}
\newacronym{oop}{OOP}{Object-Oriented Programming}
\newacronym{cdf}{CDF}{Computable Document Format}
\newacronym{mathML}{MathML}{Mathematical Markup Language}
\newacronym{cfsf}{CFSF}{Continued Fractions for Special Functions}
\newacronym{ecf}{eCF}{Encoding Continued Fraction Knowledge}
\newacronym{nist}{NIST}{National Institute of Standards and Technology}
\newacronym{vmext}{VMEXT}{Visualizing Mathematical Expression Trees}
\newacronym{opsf}{OPSF}{Orthogonal Polynomials and Special Functions}
\newacronym{wp}{WP}{Word Processor}
\newacronym{stem}{STEM}{Science, Technology, Engineering and Mathematics}
\newacronym{gui}{GUI}{Graphical User Interface}
\newacronym{omdoc}{OMDoc}{Open Mathematical Documents}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\title{
    Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Word Processors
}

@@

\begin{document}
\maketitle
\begin{abstract}
\glsresetall
\noindent
\textbf{Purpose:} Modern mathematicians and scientists of math-related disciplines use \glspl*{wp} to write and \glspl*{cas} to calculate mathematical expressions. Usually, they translate the expressions manually between \gls*{wp} and \gls*{cas}. This process is time-consuming and error-prone. Our goal is to automate this translation. This paper uses \Maple{} and \Mathematica{} as the \gls*{cas}, and \LaTeX{} as our \gls*{wp}.

@@

\section{Introduction}
A typical workflow of a scientist who writes a scientific publication is to use a \gls*{wp} to write the paper and one or more \glspl*{cas} for verification, analysis and visualization. Especially in the \gls*{stem} literature, \LaTeX\footnote{Note that technically \LaTeX{} is not a \gls*{wp} (\url{https://www.latex-project.org/about/}, seen 07/2017) like \textit{Microsoft Word}. However, since \LaTeX{} (an extension of \TeX) is the de facto standard for writing articles in \gls*{stem}, and we only focus on mathematical writing in this paper, we have categorized \LaTeX{} as a \gls*{wp} as well.} has become the de facto standard for writing scientific publications over the past 30 years~\parencites{Knuth}[559]{DigitalTypo}{LATEX:Standard}. \LaTeX{} enables printing of mathematical formulae in a structure similar to handwritten style. For example, consider the specific Jacobi polynomial~\parencite[Table 18.3.1]{NIST:DLMF}
\begin{equation}\label{eq:P}
P_n^{(\alpha , \beta)}(\cos(a\Theta)),
\end{equation}
where $n$ is a nonnegative integer, $\alpha, \beta > -1$, and $a,\Theta\in{\mathbf R}$.
This mathematical expression is written in \LaTeX{} as
\begin{equation*}
\verb|P_n^{(\alpha,\beta)}(\cos(a\Theta))|.
\end{equation*}

>>>>

\addbibresource{./bibliography/Bibliography.bib} 
\hypersetup{
	pdftitle	= {Semantic Preserving Bijective Mappings for Representations of Special Functions in Computer Algebra Systems and Document Preparation Systems}
}

@@

\newacronym{dlmf}{DLMF}{Digital Library of Mathematical Functions}
\newacronym{drmf}{DRMF}{Digital Repository of Mathematical Formulae}
\newacronym{cas}{CAS}{Computer Algebra System}
\newacronym{mlp}{MLP}{Mathematical Language Parser}
\newacronym{mlp-pt}{PPT}{PoM-Parsed Tree}
\newacronym{pom-pt}{PPT}{PoM-Parsed Tree}
\newacronym{bnf}{BNF}{Backus-Naur Form}
\newacronym{p2c}{P2C}{Presentation-To-Computation}
\newacronym{nlp}{NLP}{Natural Language Processing}
\newacronym{pom}{PoM}{Part-of-Math}
\newacronym{csv}{CSV}{Comma-Separated Values}
\newacronym{json}{JSON}{JavaScript Object Notation}
\newacronym{teo}{TEO}{Translated Expression Object}
\newacronym{pol}{NPN}{Normal Polish Notation}
\newacronym{rpol}{RPN}{Reverse Polish Notation}
\newacronym{dag}{DAG}{Directed Acyclic Graph}
\newacronym{api}{API}{Application Programming Interface}
\newacronym{mathml}{MathML}{Mathematical Markup Language}
\newacronym{oop}{OOP}{Object-Oriented Programming}
\newacronym{cdf}{CDF}{Computable Document Format}
\newacronym{mathML}{MathML}{Mathematical Markup Language}
\newacronym{cfsf}{CFSF}{Continued Fractions for Special Functions}
\newacronym{ecf}{eCF}{Encoding Continued Fraction Knowledge}
\newacronym{nist}{NIST}{National Institute of Standards and Technology}
\newacronym{vmext}{VMEXT}{Visualizing Mathematical Expression Trees}
\newacronym{opsf}{OPSF}{Orthogonal Polynomials and Special Functions}
\newacronym{dps}{DPS}{Document Preparation System}
\newacronym{stem}{STEM}{Science, Technology, Engineering and Mathematics}
\newacronym{gui}{GUI}{Graphical User Interface}
\newacronym{omdoc}{OMDoc}{Open Mathematical Documents}

@@

%%%%%%%%%%%%%%%%%%%%%%%%% INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\title{
    Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Document Preparation Systems
}

@@

\begin{document}
\maketitle
\begin{abstract}
\glsresetall
\noindent
\textbf{Purpose:} Modern mathematicians and scientists of math-related disciplines use \glspl*{dps} to write and \glspl*{cas} to calculate mathematical expressions. Usually, they translate the expressions manually between \gls*{dps} and \gls*{cas}. This process is time-consuming and error-prone. Our goal is to automate this translation. This paper uses \Maple{} and \Mathematica{} as the \gls*{cas}, and \LaTeX{} as our \gls*{dps}.

@@

\section{Introduction}
A typical workflow of a scientist who writes a scientific publication is to use a \gls*{dps} to write the paper and one or more \glspl*{cas} for verification, analysis and visualization. Especially in the \gls*{stem} literature, \LaTeX{}
%\footnote{Note that technically \LaTeX{} is not a \gls*{dps} (\url{https://www.latex-project.org/about/}, seen 07/2017) like \textit{Microsoft Word}. However, since \LaTeX{} (an extension of \TeX) is the de facto standard for writing articles in \gls*{stem}, and we only focus on mathematical writing in this paper, we have categorized \LaTeX{} as a \gls*{dps} as well.} 
has become the de facto standard for writing scientific publications over the past 30 years~\parencites{Knuth}[559]{DigitalTypo}{LATEX:Standard}. \LaTeX{} enables printing of mathematical formulae in a structure similar to handwritten style. For example, consider the specific Jacobi polynomial~\parencite[Table 18.3.1]{NIST:DLMF}
\begin{equation}\label{eq:P}
P_n^{(\alpha , \beta)}(\cos(a\Theta)),
\end{equation}
where $n$ is a nonnegative integer, $\alpha, \beta > -1$, and $a,\Theta\in{\mathbf R}$.
This mathematical expression is written in \LaTeX{} as
\begin{equation*}
\verb|P_n^{(\alpha,\beta)}(\cos(a\Theta))|.
\end{equation*}
